% Please do not change the document class
\documentclass{scrartcl}

% Please do not change these packages
\usepackage[hidelinks]{hyperref}
\usepackage[none]{hyphenat}
\usepackage{setspace}
\doublespace

% You may add additional packages here
\usepackage{amsmath}

% Please include a clear, concise, and descriptive title
\title{Comp 150 CPD Report}

% Please do not change the subtitle
\subtitle{COMP150 - CPD Report}

% Please put your student number in the author field
\author{1603294}

\begin{document}

\maketitle

\section{Introduction}

As a career I'd like to continue programming games, specifically A.I. withing games. Due to this I've found five skills key for achieving this goal. They are understanding the behavioural aspects of humans, increasing my core understaning of coding, gaing motivation for all deadlines, improving my ability to write and understand code and increasing my use and understanding of the Agile Philosophy.

\section{Understanding the behavioural aspects of humans}

To pursue a career in A.I. programming within the games indutry I will first have to understand the behavioural paterns of humans under different constraits.

\section{Increasing my core understaning of coding}

Increasing my core understanding of code is a huge skill that I must have for any kind of coding career.

\section{Gaining motivation for all deadlines}

Gaining motivation for deadlines is a key skill that I must improve in order to gain a career.

\section{Improving my ability too write and understand code}

Improving my ability too write and understanding code is a huge skill that will need adressing if I want to follow my chosen career path.

\section{Increasing my use and understanding of the Agile Philosophy}

Write about 200 words. As above.

\section{Conclusion}

Write your conclusion here. Though the conclusion should be brief, no more than 100 words, it should do more than merely summarise the report. Focus on the five SMART actions that you intend to take in order to overcome any challenges and/or obstacles. Contextualise how this will help you towards your intended career goal and how this may improve your project for the next semester.

\bibliographystyle{ieeetran}
\bibliography{references}

\end{document}
